Identification of high-yielding soybean lines with exceptional seed composition qualities

### 2022-05-09 doc/manuscript/manuscript.Rmd
Added a function to make a latex version of the yield summary table

---
title: Identification of high-yielding soybean lines with exceptional seed composition qualities
author:
  - name: Jay Gillenwater
    affil: 1,\ddagger,*
    orcid: 0000-0002-3477-6291
affiliation:
  - num: 1
    address: |
      Department of Crop and Soil Sciences, NCSU, Raleigh, NC, USA
    email: jhgille2@ncsu.edu
# firstnote to eighthnote
firstnote: |
  Current address: Updated affiliation
secondnote: |
  These authors contributed equally to this work.
correspondence: |
  leutnant@fh-muenster.de; Tel.: +XX-000-00-0000.
journal: Agronomy
type: article
status: submit
bibliography: mybibfile.bib
appendix: appendix.tex
simplesummary: |
  A Simple summary goes here.
abstract: |
  A single paragraph of about 200 words maximum. For research articles, 
  abstracts should give a pertinent overview of the work. We strongly encourage
  authors to use the following style of structured abstracts, but without 
  headings: 1) Background: Place the question addressed in a broad context and
  highlight the purpose of the study; 2) Methods: Describe briefly the main
  methods or treatments applied; 3) Results: Summarize the article's main 
  findings; and 4) Conclusion: Indicate the main conclusions or interpretations. 
  The abstract should be an objective representation of the article, it must not 
  contain results which are not presented and substantiated in the main text and 
  should not exaggerate the main conclusions.
keywords: |
  yield; protein; oil;soybean; protein meal
acknowledgement: |
  All sources of funding of the study should be disclosed. Please clearly 
  indicate grants that you have received in support of your research work. 
  Clearly state if you received funds for covering the costs to publish in open 
  access.
authorcontributions: |
  For research articles with several authors, a short paragraph specifying their 
  individual contributions must be provided. The following statements should be 
  used ``X.X. and Y.Y. conceive and designed the experiments; X.X. performed the 
  experiments; X.X. and Y.Y. analyzed the data; W.W. contributed 
  reagents/materials/analysis tools; Y.Y. wrote the paper.'' Authorship must be
  limited to those who have contributed substantially to the work reported.
conflictsofinterest: |
  Declare conflicts of interest or state 'The authors declare no conflict of 
  interest.' Authors must identify and declare any personal circumstances or
  interest that may be perceived as inappropriately influencing the
  representation or interpretation of reported research results. Any role of the
  funding sponsors in the design of the study; in the collection, analyses or 
  interpretation of data in the writing of the manuscript, or in the decision to 
  publish the results must be declared in this section. If there is no role, 
  please state 'The founding sponsors had no role in the design of the study; 
  in the collection, analyses, or interpretation of data; in the writing of the 
  manuscript, an in the decision to publish the results'.
sampleavailability: |
  Samples of the compounds ...... are available from the authors.
abbreviations:
  - short: MDPI
    long: Multidisciplinary Digital Publishing Institute
  - short: DOAJ
    long: Directory of open access journals
  - short: TLA
    long: Three letter acronym
  - short: LD 
    long: linear dichroism
output: rticles::mdpi_article
---

```{r setup, warning=FALSE,echo = FALSE, message=FALSE}
library(here)
source(here("packages.R"))
tar_load(c(example_table))
```

@@

Models were fit using the gamem_met function from the metan package[@olivotoMetanPackageMultienvironment2020]. Least-square means (LS Means) for each genotype and trait were calculated using the above model using the emmeans package[@lenthEmmeansEstimatedMarginal2022] in R. The emmeans package was also used to calculate contrasts as a post-hoc test to compare RIL means to check means. Pearson correlation coefficients between each phenotype were calculated with the cor function in R.

@@

This section may be divided by subheadings. It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.

>>>>

---
title: Identification of high-yielding soybean lines with exceptional seed composition qualities
author:
  - name: Jay Gillenwater
    affil: 1,\ddagger,*
    orcid: 0000-0002-3477-6291
affiliation:
  - num: 1
    address: |
      Department of Crop and Soil Sciences, NCSU, Raleigh, NC, USA
    email: jhgille2@ncsu.edu
# firstnote to eighthnote
firstnote: |
  Current address: Updated affiliation
secondnote: |
  These authors contributed equally to this work.
correspondence: |
  leutnant@fh-muenster.de; Tel.: +XX-000-00-0000.
journal: Agronomy
type: article
status: submit
bibliography: mybibfile.bib
appendix: appendix.tex
simplesummary: |
  A Simple summary goes here.
abstract: |
  In current markets, the primary uses for soybean seed are in products derived from 
  it's oil or protein content. However, growers are compensated based on seed oil so 
  a more valuable crop is one with both high yield, and high protein, oil, or a combination of the two. A negative 
  correlation between seed yield and seed protein makes improving these traits simultaneously difficult but 
  not impossible through conventional breeding. A selection of lines with exceptional yield and seed 
  composition qualities was made from two recombinant inbred line (RIL) soybean mapping populations to identify soybean
  varieties with yield comparable to existing cultivars, and seed composition traits superior to existing cultivars.
keywords: |
  yield; protein; oil;soybean; protein meal
acknowledgement: |
  All sources of funding of the study should be disclosed. Please clearly 
  indicate grants that you have received in support of your research work. 
  Clearly state if you received funds for covering the costs to publish in open 
  access.
authorcontributions: |
  For research articles with several authors, a short paragraph specifying their 
  individual contributions must be provided. The following statements should be 
  used ``X.X. and Y.Y. conceive and designed the experiments; X.X. performed the 
  experiments; X.X. and Y.Y. analyzed the data; W.W. contributed 
  reagents/materials/analysis tools; Y.Y. wrote the paper.'' Authorship must be
  limited to those who have contributed substantially to the work reported.
conflictsofinterest: |
  Declare conflicts of interest or state 'The authors declare no conflict of 
  interest.' Authors must identify and declare any personal circumstances or
  interest that may be perceived as inappropriately influencing the
  representation or interpretation of reported research results. Any role of the
  funding sponsors in the design of the study; in the collection, analyses or 
  interpretation of data in the writing of the manuscript, or in the decision to 
  publish the results must be declared in this section. If there is no role, 
  please state 'The founding sponsors had no role in the design of the study; 
  in the collection, analyses, or interpretation of data; in the writing of the 
  manuscript, an in the decision to publish the results'.
sampleavailability: |
  Samples of the compounds ...... are available from the authors.
abbreviations:
  - short: MDPI
    long: Multidisciplinary Digital Publishing Institute
  - short: DOAJ
    long: Directory of open access journals
  - short: TLA
    long: Three letter acronym
  - short: LD 
    long: linear dichroism
output: rticles::mdpi_article
---

```{r setup, warning=FALSE,echo = FALSE, message=FALSE}
library(here)
source(here("packages.R"))
tar_load(c(example_table, 
           yield_summary_tables))
```

@@

Models were fit using the gamem_met function from the metan package[@olivotoMetanPackageMultienvironment2020]. Least-square means (LS Means) for each genotype and trait were calculated using the above model using the emmeans package[@lenthEmmeansEstimatedMarginal2022] in R. The emmeans package was also used to calculate contrasts as a post-hoc test to compare RIL means to check means. Pearson correlation coefficients between each phenotype were calculated and visualized with the metan package.

@@

Multiple RILs in each test were identified with yield comparable to, or superior to that of the check cultivars included in each test.

```{r test1_summary_table, results = "asis", echo = FALSE}

print(yield_summary_tables$`Jay Test 1`)

```

### 2022-05-09 doc/manuscript/manuscript.tex
Added a function to make a latex version of the yield summary table

% Abstract (Do not insert blank lines, i.e. \\)
\abstract{A single paragraph of about 200 words maximum. For research
articles, abstracts should give a pertinent overview of the work. We
strongly encourage authors to use the following style of structured
abstracts, but without headings: 1) Background: Place the question
addressed in a broad context and highlight the purpose of the study; 2)
Methods: Describe briefly the main methods or treatments applied; 3)
Results: Summarize the article's main findings; and 4) Conclusion:
Indicate the main conclusions or interpretations. The abstract should be
an objective representation of the article, it must not contain results
which are not presented and substantiated in the main text and should
not exaggerate the main conclusions.}

@@

Models were fit using the gamem\_met function from the metan
package\citep{olivotoMetanPackageMultienvironment2020}. Least-square
means (LS Means) for each genotype and trait were calculated using the
above model using the emmeans
package\citep{lenthEmmeansEstimatedMarginal2022} in R. The emmeans
package was also used to calculate contrasts as a post-hoc test to
compare RIL means to check means. Pearson correlation coefficients
between each phenotype were calculated with the cor function in R.

@@

This section may be divided by subheadings. It should provide a concise
and precise description of the experimental results, their
interpretation as well as the experimental conclusions that can be
drawn.

>>>>

% Abstract (Do not insert blank lines, i.e. \\)
\abstract{In current markets, the primary uses for soybean seed are in
products derived from it's oil or protein content. However, growers are
compensated based on seed oil so a more valuable crop is one with both
high yield, and high protein, oil, or a combination of the two. A
negative correlation between seed yield and seed protein makes improving
these traits simultaneously difficult but not impossible through
conventional breeding. A selection of lines with exceptional yield and
seed composition qualities was made from two recombinant inbred line
(RIL) soybean mapping populations to identify soybean varieties with
yield comparable to existing cultivars, and seed composition traits
superior to existing cultivars.}

@@

Models were fit using the gamem\_met function from the metan
package\citep{olivotoMetanPackageMultienvironment2020}. Least-square
means (LS Means) for each genotype and trait were calculated using the
above model using the emmeans
package\citep{lenthEmmeansEstimatedMarginal2022} in R. The emmeans
package was also used to calculate contrasts as a post-hoc test to
compare RIL means to check means. Pearson correlation coefficients
between each phenotype were calculated and visualized with the metan
package.

@@

Multiple RILs in each test were identified with yield comparable to, or
superior to that of the check cultivars included in each test.

\caption{Marginal means and rankings of genotypes in Jay Test 1 for seed yield, seed oil, and seed protein.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{ccccccccccccc}
\toprule
\multicolumn{1}{c}{} & \multicolumn{4}{c}{Protein} & \multicolumn{4}{c}{Yield} & \multicolumn{4}{c}{Oil} \\
\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-9} \cmidrule(l{3pt}r{3pt}){10-13}
Genotype & Value \textbackslash{}textsuperscript\{*\} & Rank\textbackslash{}\textbackslash{}textsuperscript\{\textbackslash{}\textbackslash{}dag\} & Test Average\textbackslash{}\textbackslash{}textsuperscript\{\textbackslash{}\textbackslash{}ddag\} & Check Average\textbackslash{}\textbackslash{}textsuperscript\{\textbackslash{}\textbackslash{}S\} & Value & Rank & Test Average & Check Average & Value & Rank & Test Average & Check Average\\
\midrule
LMN09-119 & 51.37 (125.5\%) & 1 &  &  & 39.36 (87.4\%) & 18 &  &  & 18.01 (80.2\%) & 20 &  & \\
\cmidrule{1-3}
\cmidrule{6-7}
\cmidrule{10-11}
N18-1763 & 47.82 (116.8\%) & 2 &  &  & 39.45 (87.6\%) & 17 &  &  & 19.58 (87.2\%) & 18 &  & \\
\cmidrule{1-3}
\cmidrule{6-7}
\cmidrule{10-11}
N18-1855 & 47.52 (116.1\%) & 3 &  &  & 43.17 (95.8\%) & 10 &  &  & 20.6 (91.8\%) & 14 &  & \\
\cmidrule{1-3}
\cmidrule{6-7}
\cmidrule{10-11}
N18-1595 & 47.36 (115.7\%) & 4 &  &  & 43.52 (96.6\%) & 9 &  &  & 19.52 (86.9\%) & 19 &  & \\
\cmidrule{1-3}
\cmidrule{6-7}
\cmidrule{10-11}
Dunphy & 41.71 (101.9\%) & 18 &  &  & 47.33 (105.1\%) & 1 &  &  & 21.52 (95.9\%) & 4 &  & \\
\cmidrule{1-3}
\cmidrule{6-7}
\cmidrule{10-11}
Dilday & 41.22 (100.7\%) & 19 &  &  & 46.78 (103.8\%) & 2 &  &  & 22.33 (99.5\%) & 2 &  & \\
\cmidrule{1-3}
\cmidrule{6-7}
\cmidrule{10-11}
N18-1632-2 & 46.67 (114\%) & 5 &  &  & 46.34 (102.9\%) & 5 &  &  & 20.8 (92.7\%) & 11 &  & \\
\cmidrule{1-3}
\cmidrule{6-7}
\cmidrule{10-11}
N18-1632-1 & 46.64 (113.9\%) & 6 &  &  & 45.73 (101.5\%) & 6 &  &  & 20.76 (92.5\%) & 12 &  & \\
\cmidrule{1-3}
\cmidrule{6-7}
\cmidrule{10-11}
N18-1620 & 43.63 (106.6\%) & 15 &  &  & 46.54 (103.3\%) & 3 &  &  & 21.4 (95.3\%) & 6 &  & \\
\cmidrule{1-3}
\cmidrule{6-7}
\cmidrule{10-11}
N18-1635 & 43.61 (106.5\%) & 16 &  &  & 46.45 (103.1\%) & 4 &  &  & 21.72 (96.7\%) & 3 &  & \\
\cmidrule{1-3}
\cmidrule{6-7}
\cmidrule{10-11}
N09-09 & 46.31 (113.1\%) & 7 &  &  & 41.61 (92.4\%) & 14 &  &  & 19.77 (88.1\%) & 17 &  & \\
\cmidrule{1-3}
\cmidrule{6-7}
\cmidrule{10-11}
N18-1731 & 46.1 (112.6\%) & 8 &  &  & 43.16 (95.8\%) & 11 &  &  & 20.49 (91.3\%) & 15 &  & \\
\cmidrule{1-3}
\cmidrule{6-7}
\cmidrule{10-11}
N18-1674 & 45.19 (110.4\%) & 9 &  &  & 44.26 (98.2\%) & 7 &  &  & 21.21 (94.5\%) & 9 &  & \\
\cmidrule{1-3}
\cmidrule{6-7}
\cmidrule{10-11}
N18-1682 & 45.11 (110.2\%) & 10 &  &  & 43.64 (96.9\%) & 8 &  &  & 20.76 (92.5\%) & 13 &  & \\
\cmidrule{1-3}
\cmidrule{6-7}
\cmidrule{10-11}
N18-1572 & 45.08 (110.1\%) & 11 &  &  & 38.58 (85.6\%) & 19 &  &  & 21.19 (94.4\%) & 10 &  & \\
\cmidrule{1-3}
\cmidrule{6-7}
\cmidrule{10-11}
N18-1751 & 44.8 (109.4\%) & 12 &  &  & 41.59 (92.3\%) & 15 &  &  & 20.44 (91\%) & 16 &  & \\
\cmidrule{1-3}
\cmidrule{6-7}
\cmidrule{10-11}
N18-1956 & 44.55 (108.8\%) & 13 &  &  & 34.79 (77.2\%) & 20 &  &  & 21.51 (95.8\%) & 5 &  & \\
\cmidrule{1-3}
\cmidrule{6-7}
\cmidrule{10-11}
N18-1604 & 43.83 (107.1\%) & 14 &  &  & 43.15 (95.8\%) & 12 &  &  & 21.34 (95.1\%) & 8 &  & \\
\cmidrule{1-3}
\cmidrule{6-7}
\cmidrule{10-11}
N18-1641 & 43.33 (105.8\%) & 17 &  &  & 41.99 (93.2\%) & 13 &  &  & 21.36 (95.1\%) & 7 &  & \\
\cmidrule{1-3}
\cmidrule{6-7}
\cmidrule{10-11}
NC-Raleigh & 39.91 (97.5\%) & 20 & \multirow{-20}{*}{\centering\arraybackslash 45.09} & \multirow{-20}{*}{\centering\arraybackslash 40.94} & 41.04 (91.1\%) & 16 & \multirow{-20}{*}{\centering\arraybackslash 42.92} & \multirow{-20}{*}{\centering\arraybackslash 45.05} & 23.5 (104.7\%) & 1 & \multirow{-20}{*}{\centering\arraybackslash 20.89} & \multirow{-20}{*}{\centering\arraybackslash 22.45}\\
\bottomrule
\multicolumn{13}{l}{\rule{0pt}{1em}\textsuperscript{*} Observed marginal mean of the phenotype (value of the phenotype/check average * 100\%).}\\
\multicolumn{13}{l}{\rule{0pt}{1em}\textsuperscript{\dag} Rank of the genotype within the particular phenotype.}\\
\multicolumn{13}{l}{\rule{0pt}{1em}\textsuperscript{\ddag} The average value of the phenotype for all lines in the test.}\\
\multicolumn{13}{l}{\rule{0pt}{1em}\textsuperscript{\S} The average value of the phenotype for the checks in the test.}\\
\end{tabular}}
\end{table}
